\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-12-08 review-responses.tex

\begin{point}{\revref}
Definition \ref{def:lineage_generator}, Proposition 2.23: I think these may need to be rewritten/rephrased. Up
to Proposition \ref{thm:lineages}, it is not clear what ``that individual'' is in the limiting model. Therefore,
it is not clear what $L_s$ is. While the definition of the process $L^N$ maybe clear, what is the
precise definition of $L_s$ ? I think these need to be defined through the finite-$N$ models. It may
be good to explain why the process $L$ is Markovian, or at least point out that it is Markovian,
before talking about semigroup. Probably Section \ref{sec:lineage_motion} will need to be modified accordingly.
\end{point}

\reply{
    Add sentence saying that this is well-defined because we take the finite-$N$ limit.
    Markovian because it is conditional on the population process, which is deterministic...
}

\begin{point}{\revref}
The two conditions in equation \eqref{conditions for one step} are crucial for the one-step convergence.
It would be great to mention exactly where each of them are used in Section \ref{subsec:one step convergence proof}.
A brief explanation about these conditions would also be nice. For example, it seems the first (high
migration/mixing rate) condition in \eqref{conditions for one step},
but not the second (high density) condition, is used
to guarantees that $\psi_t^{\epsilon,x}$ is close to a heat kernel?
\end{point}

\reply{
    Add discussion of that here.
    (in particular the one condition comes from the crucial lemma 7.2)
}

@@

\begin{point}{\revref}
% P32 third line in Section 5.3:
    Pointwise in time?
\end{point}

\reply{
    $\omega$
}

\begin{point}{\revref}
Proposition \ref{prop:limiting_construction}: In ``For any solution to the equation above'', what is a ``solution''? Is it
a solution for all time? Also, be specific to ``the equations above'' by labeling and referring
to the precise equations including the unlabeled displayed equation below \eqref{eqn:limiting_construction}.
\end{point}

\reply{
    Let $X$, $U$ be solutions to 5.20 on $[0,T]$... then $\eta$ is a solution on $[0,T]$...
}

@@

\begin{point}{\revref}
%    P48:
    The notation $\mathcal{O}(\epsilon)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
    Alison TODO
}

\begin{point}{\revref}
% P54: near the bottom:
    Can you be more specific what in paper \citet{barlow/jacka/yor:1986} is being used here?
\end{point}

\reply{
    that we can bound the expectation of the quadratic variation by a constant times the expectation of the angle bracket process
    (AS BEFORE)
}

@@

\begin{point}{\revref}
% P60:
The notation $\mathcal{O}(\delta)$ seems to first appear here. Please explain its meaning. Do they
depend on x?
\end{point}

\reply{
    Point out we're using 7.2 with $u=0$ and our assumptions about initial conditions.
    (and maybe write that it's less than a constant times $\delta$;)
}
